A significance test in forward stepwise model selection

### 2014-05-12 paper/paper.tex
abstract update

\begin{abstract}
% perhaps de-emphasize group LASSO and emphasize forward stepwise?
  We extend the methods developed by \cite{significance:lasso} and
  \cite{tests:adaptive} on significance tests for penalized
  regression to stepwise model selection by iteratively applying
  the global null hypothesis test on the residual in a forward stepwise
  procedure. While not fully theoretically justified, the resulting method
  has the computational strengths of stepwise selection and partially
  solves the problem of inflated test statistics due to model selection.
  We illustrate the flexibility of this method by applying it to
  novel specialized applications of forward stepwise to a hierarchically
  constrained interactions model and generalized additive models.
\end{abstract}

>>>>

\begin{abstract}
% perhaps de-emphasize group LASSO and emphasize forward stepwise?
  We extend the methods developed by \cite{significance:lasso} and
  \cite{tests:adaptive} on significance tests for penalized
  regression to stepwise model selection by iteratively applying
  the global null hypothesis test on the residual in a forward stepwise
  procedure. The resulting method
  has the computational strengths of stepwise selection and partially
  solves the problem of inflated test statistics due to model selection.
  In describing our variant of forward stepwise selection, we introduce
  a new class of selection procedures, described by quadratic inequalities and
  provide an algorithm that can be used for exact post-selection inference for such problems.

  We illustrate the flexibility of our procedure by applying it to
  novel specialized applications of forward stepwise to a hierarchically
  constrained interactions model and recently described flexible additive models
  that choose between linear and nonlinear effects for each variable.
\end{abstract}
